\sys: Automated Data-Parallel Shell Processing

### 2020-04-07 pldi/draft.tex
Comments and notes on unix50 pipelines that have no speedup

The goal of this subsection is to evaluate \sys on an existing set of
unix pipelines found in the wild. \todo{Motivate why unix50 is a nice
  set of pipelines.} We took the solutions for the unix50 from
\todo{Ref} and we executed them \emph{without any modification} with
\sys's parallelism set to \todo{X}. The input given to the pipelines
was the test input from unix50 multiplied \todo{10000} times. The
speedup of each pipeline separately is shown in \todo{ref}. The
average\todo{/median} speedup is \todo{X}.

>>>>

The goal of this subsection is to evaluate \sys on an existing set of
unix pipelines found in the wild. \todo{Motivate why unix50 is a nice
  set of pipelines.} We took the solutions for the unix50 from
\todo{Ref} and we executed them \emph{without any modification} with
\sys's parallelism set to \todo{20}. The input given to the pipelines
was the test input from unix50 multiplied \todo{10000} times. The
speedup of each pipeline separately is shown in
\Cref{fig:unix50-individual}. The average\todo{/median} speedup is
\todo{5.24}.

%% The current average speedup includes unimplemented and small input pipelines.

%% Bad result descriptions:
%%  2. Contains just a head -n 2, and then a cut.
%%  5. Very fast (small input). Sequential time is 0m0.103s (If we increase the input we will show speedup)
%%  18. TODO: Implement
%%  20. Four corners (not parallelizable). So performance is reasonable
%%      (atm it doesn't return the correct result for multiplied input though)
%%  21. Last capital character of each line. Their solution is not general (and it is not parallelizable).
%%      Also, the input is very small. Changing it to a more general one and
%%      increasing input size leads to speedup. TODO: Run with large input
%%  22. Exactly the same problem as the above.
%%  24. (Not sure: It seems that the computation is trivial)
%%  32. TODO: Implement

%% WARNING: Remember to fix `sed` and not have it be stateless in general.

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{\detokenize{./figs/unix50_individual_speedups_20.pdf}}
  \caption{
    \textbf{Speedup achieved by \sys for all pipelines with parallelism 20.}
    \todo{Scale the 0-1 region of the yaxis as much as the 1-20.}}
  \vspace{-15pt}
  \label{fig:unix50-individual}
\end{figure}
